Modal type theory based on the intuitionistic epistemic logic

### 2018-01-14 article.tex
added
Revert "added rewrite"
This reverts commit 82d65e58f1e2ae7113751d29f684b3a94ca5ce90.

  	\begin{prooftree}
    	\AxiomC{$\Gamma, \Delta \vdash A$}
    	\RightLabel{$\vdash {\bf K}_I$}
    	\UnaryInfC{${\bf K}(\Gamma), \Delta \vdash {\bf K}A$}
  \end{prooftree}
    \end{flushleft}
  \end{minipage}
  \begin{minipage}{0.5\textwidth}
    \begin{flushright}
    	\begin{prooftree}
  	\AxiomC{$\Gamma \vdash A \to B$}
  	\AxiomC{$\Gamma \vdash A$}
  	\RightLabel{$\rightarrow_i$}
  	\BinaryInfC{$\Gamma \vdash B$}
    	\end{prooftree}

@@

  	\begin{prooftree}
    \AxiomC{${\bf K}(\Gamma), \Delta \vdash {\bf K} A$}
    \AxiomC{${\bf K}(\Gamma), {\bf K} A, \Delta \vdash B$}
    \BinaryInfC{${\bf K}(\Gamma), \Delta \vdash B$}
  	\end{prooftree}
    \end{flushright}
  \end{minipage}
  \end{defin}

@@

1) If $\Gamma, \Delta \vdash_{NIEL^{-}_{\land, \to}} A$, then $IEL^{-} \vdash \bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta \rightarrow {\bf K}A$.

See \cite{Krupski}.

@@

2) If ${\bf K} \Gamma, \Delta \vdash_{NIEL^{-}_{\land, \to}} {\bf K} A$ and ${\bf K}\Gamma, {\bf K} A, \Delta \vdash B$, then $IEL^{-} \vdash \bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta \rightarrow B$.

$\begin{array}{lll}
&\text{(1) } \bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta \to {\bf K} A& \text{assumption} \\
&\text{(2) } \bigwedge {\bf K} \Gamma \wedge {\bf K}A \wedge \bigwedge \Delta \rightarrow B& \text{assumption} \\
&\text{(3) } {\bf K} A \wedge (\bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta) \rightarrow B& \text{conjuction properties} \\
&\text{(4) } ({\bf K} A \wedge (\bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta) \rightarrow B) \rightarrow ({\bf K } A \rightarrow ((\bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta) \rightarrow B)) & \text{IPC theorem} \\
&\text{(5) } {\bf K} A \rightarrow ((\bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta) \rightarrow B) & \text{MP } \\
&\text{(6) } \bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta \to ((\bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta) \rightarrow B) & \text{(1), (5), transitivity} \\
&\text{(7) } (\bigwedge {\bf K} \Gamma \wedge \bigwedge \Delta) \rightarrow B & \text{(6), contraction}
\end{array}$

@@

  \begin{lemma}
    $ $

    If $\text{IEL}^{-} \vdash A$, then $\text{NIEL}^{-} \vdash A$.
  \end{lemma}

  \begin{proof}
    $ $
    Straightforward derivation of modal axioms in NIEL.
  \end{proof}

@@

  We divide into two parts, the first one zone is a modal part (enviroment with applicaitve types), the second one
  is a intuitionistic part (enviroment with pure types). From a logical point of view, $\Gamma | \Delta \vdash M : A$ denotes that
  $M$ is a proof of ${\bf K} \Gamma, \Delta \vdash A$. This idea similar to \cite{DePaiva}.

@@

$\begin{array}{lll}
&\text{1) } (\lambda x. M) N \rightarrow_{\beta} M [x := N]& \\
&\text{2) } \pi_1 \langle M, N \rangle \rightarrow_{\beta} M& \\
&\text{3) } \pi_2 \langle M, N \rangle \rightarrow_{\beta} N& \\
\end{array}$

@@

  \bibitem{Baren2} H.P. Barendregt. The Lambda Calculus --- Its Syntax and Semantics. Studies in Logic and
  the Foundations of Mathematics, vol. 103. Amsterdam: North-Holland, 1985.

  \bibitem{DePaiva} de Paiva V., Ritter E., Bellin, G. Extended Curry-Howard correspondence for a basic constructive modal logic. Methods for Modalities Conference (M4M-2); 2001 November 29-30; Amsterdam; the Netherlands.
\end{thebibliography}

>>>>

  	\begin{prooftree}
    	\AxiomC{$\Gamma \vdash A$}
    	\RightLabel{$\textbf{K}_I$}
    	\UnaryInfC{$\Gamma \vdash \textbf{K}A$}
  \end{prooftree}
    \end{flushleft}
  \end{minipage}
  \begin{minipage}{0.5\textwidth}
    \begin{flushright}
    	\begin{prooftree}
  	\AxiomC{$\Gamma \vdash A \to B$}
  	\AxiomC{$\Gamma \vdash A$}
  	\RightLabel{$\rightarrow_i$}
  	\BinaryInfC{$\Gamma \vdash B$}
    	\end{prooftree}

@@

  	\begin{prooftree}
    \AxiomC{$\Gamma \vdash {\bf K} \vec{A}$}
    \AxiomC{$\vec{A} \vdash B$}
    \BinaryInfC{$\Gamma \vdash {\bf K} B$}
  	\end{prooftree}
    \end{flushright}
  \end{minipage}
  \end{defin}

Where $\Gamma \vdash {\bf K} \vec{A}$ is a syntax sugar for $\Gamma \vdash {\bf K} A_1 ,\dots, \Gamma \vdash {\bf K} A_n$.

@@

1) If $\Gamma \vdash_{NIEL^{-}_{\land, \to}} A$, then $IEL^{-} \vdash \bigwedge \Gamma \rightarrow \textbf{K}A$.

$\begin{array}{lll}
(1) & \bigwedge \Gamma \rightarrow A & \text{assumption}\\
(2) & A \rightarrow \textbf{K}A &\text{co-reflection}\\
(3) & (\bigwedge \Gamma \rightarrow A) \rightarrow ((A \rightarrow \textbf{K}A) \rightarrow (\bigwedge \Gamma \rightarrow \textbf{K}A))&\text{IPC theorem}\\
(4) & (A \rightarrow \textbf{K}A) \rightarrow (\bigwedge \Gamma \rightarrow \textbf{K}A) &\text{from (1), (3) and MP}\\
(5) & \bigwedge \Gamma \rightarrow \textbf{K}A &\text{from (2), (4) and MP}\\
\end{array}$

@@

2) If $\Gamma \vdash_{NIEL^{-}_{\land, \to}} {\bf K} \vec{A}$ and $\vec{A} \vdash B$, then $IEL^{-} \vdash \bigwedge \Gamma \rightarrow \textbf{K}B$.

$\begin{array}{lll}
(1) &\bigwedge \Gamma \rightarrow \bigwedge \limits_{i = 1}^{n} {\bf K} A_i & \text{assumption} \\
(2) &\bigwedge \limits_{i = 1}^{n} {\bf K} A_i \rightarrow {\bf K} \bigwedge \limits_{i = 1}^{n} A_i& \text{IEL theorem} \\
(3) &\bigwedge \Gamma \rightarrow {\bf K} \bigwedge \limits_{i = 1}^{n} A_i & \text{from (1), (2) and transitivity} \\
(4) &\bigwedge \limits_{i = 1}^{n} A_i \rightarrow B& \text{assumption} \\
(5) &(\bigwedge \limits_{i = 1}^{n} A_i \rightarrow B) \rightarrow {\bf K} (\bigwedge \limits_{i = 1}^{n} A_i \rightarrow B)& \text{co-reflection}\\
(6) &{\bf K} (\bigwedge \limits_{i = 1}^{n} A_i \rightarrow B)& \text{from (2), (3) and MP} \\
(7) &{\bf K} \bigwedge \limits_{i = 1}^{n} A_i \rightarrow {\bf K} B & \text{from (6) and normality} \\
(8) &\bigwedge \Gamma \rightarrow {\bf K} B & \text{from (3), (7) and transitivity}
\end{array}$

@@

@@

@@

$\begin{array}{lll}
&\text{1) } (\lambda x. M) N \rightarrow_{\beta} M [x := N]& \\
&\text{2) } \pi_1 \langle M, N \rangle \rightarrow_{\beta} M& \\
&\text{3) } \pi_2 \langle M, N \rangle \rightarrow_{\beta} N& \\
&\text{4) } {\bf let \: pure \: } \vec{y} = \vec{M_2} {\bf \: in \: } ({\bf let \: pure \: } \vec{x} = \vec{M_1} {\bf \: in \: }  N) \rightarrow_{\beta}& \\
&\quad {\bf let \: pure \: } \vec{x} = ({\bf let \: pure \: } \vec{y} = \vec{M_2} \: {\bf in} \: \vec{M_1}) \: {\bf in} \: {\bf let \: pure \: } \vec{x} = \vec{x} {\bf \: in \:} N&
\end{array}$

@@

  \bibitem{Baren2} H.P. Barendregt. The Lambda Calculus --- Its Syntax and Semantics. Studies in Logic and
  the Foundations of Mathematics, vol. 103. Amsterdam: North-Holland, 1985.
  \end{thebibliography}
